Variable Selection

### 2015-06-26 var_select.rmd
cforests

mini.core3 <- all7b %>%
        select(Discipline , inv.mlsto , Business,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol, pc.director,
        pc.pro , code.director , ProjEng.Pos,
        client.meaninv , client.neginv , client.numinv , client.totinv)

@@

Try running a cforest over night with full dataset - don't include 
```

@@

var.imp4<- varimp(all.cfor) %>% as.data.frame
colnames(var.imp4)[names(var.imp4) %in% '.']<-'var.imp'
var.imp4$var <- rownames(var.imp4)
#reorder levels for bar plot
var.imp4 <- within(var.imp4, 
                    var <- factor(var,levels=
                                            var.imp4[order(-abs(var.imp4$var.imp)),]$var))

q<- ggplot(data=var.imp4, aes(x=var, y=var.imp)) + theme(axis.text.x=element_text(angle=45,hjust=1))
q + geom_bar(stat='identity', position = 'dodge')

save(all.cfor,file= 'C:/Users/n9232371/Documents/github/consult/object/all_cfor.RData')
load('C:/Users/n9232371/Documents/github/consult/object/all_cfor.RData')
```

From analysing all jobs including 2009 and beyond, the most important variables are:
`levels(var.imp4$var)[1:10] %>% as.data.frame`

The least important are 
`levels(var.imp4$var)[11:19]`

@@

See how variable selection goes with random forest first, then probably just run cforest again without code.client and contact.code

>>>>

mini.core3 <- all7b %>%
        select(Discipline , inv.mlsto , Business, client.count,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol, pc.director,
        pc.pro , code.director , ProjEng.Pos,
        client.meaninv , client.neginv , client.numinv , client.totinv)

@@

Try running a cforest over night with full dataset - don't include

@@

var.imp<- varimp(all.cfor2) %>% as.data.frame
colnames(var.imp)[names(var.imp) %in% '.']<-'imp'
var.imp$var <- rownames(var.imp)
#reorder levels for bar plot
var.imp <- within(var.imp, 
                    var <- factor(var,levels=
                                            var.imp[order(-abs(var.imp$imp)),]$var))

q<- ggplot(data=var.imp, aes(x=var, y=imp)) + theme(axis.text.x=element_text(angle=45,hjust=1))
q + geom_bar(stat='identity')

save(all.cfor2,file= 'C:/Users/n9232371/Documents/github/consult/object/all_cfor2.RData')
load('C:/Users/n9232371/Documents/github/consult/object/all_cfor2.RData')

From analysing all jobs including 2009 and beyond, the most important variables are:
`levels(var.imp$var) %>% as.data.frame %>% slice(1:8)`

The least important are 
`levels(var.imp4$var) %>% as.data.frame %>% slice(9:16)`

@@

Keep:

* inv.mlsto
* timespan
* no.users
* Discipline
* pc.pro
* client.totinv
* client.numinv
* pc.director
* code.director
* Num.disc
* Business
* Biz.type

Dump

* client.neginv
* client.count
* ProjEng.Pos
* Biz.size
* client.meaninv
